AD Target Gene Report

### 2020-04-27 code/03-Run.Rmd
Partials

for( i in 1:dim(Tab)[1]){
  if(  Tab$start_position[i] < Tab$ensembl_gene_id[i] ){
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])-1e6, "-", as.numeric(Tab$end_position[i])+1e6)
  }else{
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])+1e6, "-", as.numeric(Tab$end_position[i])-1e6)
  }
}
```

>>>>

for( i in 1:dim(Tab)[1]){
  if(  Tab$start_position[i] < Tab$ensembl_gene_id[i] ){
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])-1e6, "-", as.numeric(Tab$end_position[i])+1e6)
  }else{
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])+1e6, "-", as.numeric(Tab$end_position[i])-1e6)
  }
}
Tab <- Tab[ Tab$chromosome_name %in% c( c(1:22), "X","Y"), ]
```
